Pitfall of Prediction-orienterd Machine Learning Methods and Economic Value of Statistical Efficiency in On-farm Precision Experimentation

### 2022-02-21 Writing/manuscript.rmd
change in lm ser

It is also interesting to compare the OLS and SER results. It is well-established that SER is more statistically efficient than simple OLS in the presence of unknown spatial data autocorrrelation, which is a very common in OFPE data. This advantage of SER does not seem to have received much attention as it is just a statistical property, economist have a tendency to focus on unbiasedness and consistency issues more than efficiency. However, in the context of site-specific EONR estiamtion, statistical efficiency means money. The more accurately estimated coefficients are, the more accurately site-specific EONRs are estimated, leading to a higher profit.

- However, since it is only an efficiency issue, and SER does not correct for bias, this advantage of SER model has not received enough attention. The efficiency improvement is only regarded as a statistical property, while its economic benefit is not well recognized.
- Our simulation evidence showed that the statistical efficiency of SER model can actually translate into considerable more profitable EONR recommendations. The profit of SER model is higher than OLS model by $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$ for large, medium, and small fields, respectively.
- So, using SER model to update the OLS model is likely to be economically beneficial in on-farm experimental data analysis, and should be encouraged.

>>>>

It is also interesting to compare the OLS and SER results. It is well-established that SER is more statistically efficient than simple OLS in the presence of unknown spatial data autocorrrelation, which is a very common in OFPE data. This advantage of SER does not seem to have received much attention as it is just a statistical property, economist have a tendency to focus on unbiasedness and consistency issues more than efficiency. However, in the context of site-specific EONR estiamtion, statistical efficiency means money. The more accurately estimated coefficients are, the more accurately site-specific EONRs are estimated, leading to a higher profit. While \@ref(anselin) bluh bluh, they did not do it right. Our results show that improving statistical efficiency by taking into account the spatial autocorrelation of the error term can lead to a substantial increase in profit by VRA. The profit of SER model is higher than OLS model by $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$ for large, medium, and small fields, respectively. To our knowledge,
